Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-08-27 prop_letter.tex
prop_letter.tex \section{Kochen-Specker} Updating the proof...

If a QIVPM~$\bar{\mu}$ is 0-deterministic, then for a family of
$M$ commuting observables~$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{M}$,
they can be diagonalized by a common orthonormal basis~$\Omega=\left\{ \ket{k}\right\} _{k=0}^{d-1}$.
By restricting to the commuting subspace of events~$\set{\sum_{\ket{k}\in E}\proj{k}}{E\subseteq\Omega}$,
the quantum expectation values of the observables~$\expval{\mathbf{O}_{j}}_{\bar{\mu}}$
and the product observables~$\expval{\prod_{j=1}^{M}\mathbf{O}_{j}}_{\bar{\mu}}$
are equal to the Choquet integral of the corresponding random variables
relative to the 0-deterministic classical IVPM~$\bar{\mu}'$ corresponding
to $\bar{\mu}$. The Choquet integral relative to 0-deterministic
$\bar{\mu}'$ is a singleton set. If we adopt the product rule of
singleton sets, $\left\{ x_{0}\right\} \cdot\left\{ x_{1}\right\} =\left\{ x_{0}x_{1}\right\} $,
we can can prove that the product of expectation values of the individual
observables relative to $\bar{\mu}$ is the expectation value of the
product of the family relative to $\bar{\mu}$~\citep{HOSTunpublished}:
\begin{equation}
\prod_{j=1}^{M}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j=1}^{M}\mathbf{O}_{j}}_{\bar{\mu}}\label{eq:Kochen-Specker-Rules}
\end{equation}
because the Choquet integral relative to 0-deterministic $\bar{\mu}'$
has the corresponding property.

>>>>

If a QIVPM~$\bar{\mu}$ is 0-deterministic, then for a family of
$M$ commuting observables~$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{M}$,
they can be diagonalized by a common orthonormal basis~$\Omega$.
By restricting to the subspace of commuting events generated by the
set of projectors associated with $\Omega$, the quantum expectation
values of the observables~$\expval{\mathbf{O}_{j}}_{\bar{\mu}}$
and the product observables~$\expval{\prod_{j=1}^{M}\mathbf{O}_{j}}_{\bar{\mu}}$
are equal to the Choquet integral of the corresponding random variables
relative to the 0-deterministic classical IVPM~$\bar{\mu}'$ corresponding
to $\bar{\mu}$~\citep{HOSTunpublished}. The Choquet integral relative
to 0-deterministic $\bar{\mu}'$ is a singleton set which have an
intuitive the product rule $\left\{ x_{0}\right\} \cdot\left\{ x_{1}\right\} =\left\{ x_{0}x_{1}\right\} $.
Because the product of the Choquet integrals of individual random
variables relative to $\bar{\mu}'$ is the Choquet integral of the
product of the family relative to $\bar{\mu}'$, we can then prove
that the expectation values of the observables has the corresponding
property: 
\begin{equation}
\prod_{j=1}^{M}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j=1}^{M}\mathbf{O}_{j}}_{\bar{\mu}}\,.\label{eq:Kochen-Specker-Rules}
\end{equation}
